A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-29 12_conclusions_future_work.tex
list of concluding remarks

\section{Conclusion and future work}
conclusion: reiterate abstract

@@

Generate thicker bead widths near sharp corners in order to mimic limitations in the extrusion process.

>>>>

\section{Conclusion and future work}

\begin{itemize}
\item Accurate filling using few/small overfill and underfill areas
\item Which allows for accurate reproduction of thin parts and variable thickness microstructures.
\item Our framework is able to emulate several previously proposed methods
\item Our framework allows for deposition width control which reduces the amount of extrusion paths with wildly different width compared to previous methods
\item Our framework allows for limiting the stretch on the outer toolpath in order to reduce any adverse affect of variable extrusion width on dimensional accuracy.
\item The computation times are approximately 3 times as fast as the state of the art method for naive toolpath generation employing constant width
\item (depending on what we do in the validation chapter) The produced parts employing our method are more stiff compared to other methods.
\end{itemize}

@@

Generate thicker bead widths near sharp corners in order to mimic limitations in the extrusion process.
Allow for adjusting the toolpath widths to local part curvature.

Allow for information sharing between the layers.
